---
title: "CarpentriesSlides"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CarpentriesSlides}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
resource_files:
  - git-novice/slides.md
  - git-novice/slides.html
---

```{css, echo=FALSE}
pre.markdown {
  max-height: 300px;
  overflow-y: auto;
}
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette, we'll use the [Git Novice](https://github.com/swcarpentry/git-novice) lesson as an example.

First, we need to obtain a copy of a Carpentries lesson:

```{bash}
git clone https://github.com/swcarpentry/git-novice.git
```

Then in R, we can convert the whole lesson to a markdown document:
```{r}
CarpentriesSlides::make_md("git-novice")
```

At this point, the path to the markdown presentation has been printed out, so we can manually edit the slides.
For example, we might want to remove certain figures that we don't think are essential to the presentation.
In particular, figures that demonstrate how to use a GUI application are generally not useful in the slides, because this usage should be demonstrated using live coding.

Here is an example of the generated markdown:
```{markdown}
#| eval: FALSE
#| file: git-novice/slides.md
```

Once we're happy with the content, we can convert the markdown to a Reveal JS slideshow, which is an HTML page:

```{r}
CarpentriesSlides::make_reveal("git-novice")
```

Here is a preview of the resulting slides:
```{R}
#| echo: FALSE
# Preview the slides
slides <- normalizePath("git-novice/slides.html")
glue::glue("file://{slides}") |> knitr::include_url()
```
